

\chapter*{Acknowledgements}

First and foremost, I thank Prof. Ed Moran, who took on the role as my research and thesis mentor.
Thank you for the many hours that you gave up to constantly support, advice, and teach me.
Everything I know so far about research, I owe to you.
I am eternally grateful for you for giving me my start in the world of Astronomy research.


I thank Prof. Meredith Hughes for allowing me to enroll in her ASTR155 course two weeks after the semester had started and a few days before add/drop would closed.
Having never been exposed to Astronomy before, you are the reason I fell in love with the subject and continued to pursue it.

I thank Prof. Seth Redfield for his support as a major advisor and as a TA mentor.
Thank you for pushing me to teach in front of your ASTR105 class. 
I hope to be able to teach in front of my own class in the future.

I thank Prof. Roy Kilgard for always being available to share your X-ray wisdom with me.
Thank you also for all your IT support.
I likely would have done some real damage to my basement desktop otherwise.

I thank Prof. Bill Herbst for bringing the department together at your annual fourth of July gathering.
I had the pleasure of being your student in two courses. 
Thank you for all the knowledge you have shared with me.
If this is one of the last thesis you have to read, I hope you think it's a good one.


I thank my fellow classmates and friends who I have shared wonderful memories with at Van Vleck Observatory and who were there for me whenever I needed.
Some of you were quite literally at VVO with me until the crack of dawn sometimes.


I thank all of the McNair staff for their support and guidance. 
Without their help, this work would not have been possible.
\newpage

\vspace*{\fill}
Lastly, to the COVID-19 healthcare workers and essential workers, including my mom and dad. 
While this thesis is one of the most challenging things I have had to do, the challenge pales in comparison to the challenge they face everyday.
Thank you for all your hard work.
\vspace*{\fill}




\titlespacing*{\chapter}{0pt}{*2}{*3}
